Manuscript draft

### 2019-05-29 manuscript/manuscript draft.Rmd
manuscript draft

---
title: "Untitled"
output: html_document
bibliography: library.bib
---

### Methods  
1.	ForC database [@Anderson-Teixeira2018]
+ Used data compiled from existing literature
+ 
2.	Climate data
+	WorldClim [@Hijmans2005]; WorldClim 2: vapour pressure and solar radiation [@Fick2017]
+	CRU: cloud cover; annual frost days; potential evapotranspiration; annual wet days [@Harris2014]
+	Global Aridity Index and Potential Evapotranspiration Climate Database [@Trabucco2018]
+	TerraClimate: vapour pressure deficit [@Abatzoglou2018]
3.	Run models in R
+ Model specification: mixed model using the lme4 package in R. 
+ Model = response_variable ~ fixed_variable + altitude + (1/geographic_area/plot_name), weighted by koeppen climate area

#### Database  
Analyses were conducted on data contained in the open-access ForC database [@Anderson-Teixeira2016; @Anderson-Teixeira2018]. This database contains records of field-based measurements of forest carbon stocks and annual fluxes, compiled from previously published studies and existing databases (e.g. ORNL DAAC; Luyssaert etc?). Additional targeted literature searches were conducted to identify any further available data on primary productivity, with particular focus on old-growth forests in temperate and boreal regions.

@@

*Model specification.* The effects of climate and latitude on primary productivity were analysed using mixed effects models using the package 'lme4' in R v. 1.1.463 (cite). The effect of each extracted climate variable on each measure of primary productivity was modelled by specifying the climate variable as a fixed effect. Site altitude was also included as a fixed effect. Random effect was stand nested within area. Data from the temperate regions was heavily skewed towards studies from the old-growth forests of the Pacific Northwest. These forests have very high productivity, and so to reduce any bias from over-sampling of this region, the models were weighted according to the proportion of forest cover by Koeppen climate zone.

>>>>

---
title: "Manuscript draft"
output: html_document
bibliography: library.bib
---

### Introduction

### Methods

Analyses were conducted on data contained in the open-access ForC database [@Anderson-Teixeira2016; @Anderson-Teixeira2018]. This database contains records of field-based measurements of forest carbon stocks and annual fluxes, compiled from previously published studies and existing databases (e.g. ORNL DAAC; Luyssaert etc?). Additional targeted literature searches were conducted to identify any further available data on primary productivity, with particular focus on old-growth forests in temperate and boreal regions.

@@

*Model specification.* The effects of climate and latitude on primary productivity were analysed using mixed effects models using the package 'lme4' in R v. 1.1.463 (cite). The effect of each extracted climate variable on each measure of primary productivity was modelled by specifying the climate variable as a fixed effect. Site altitude was also included as a fixed effect. Random effect was stand nested within area. Data from the temperate regions was heavily skewed towards studies from the old-growth forests of the Pacific Northwest. These forests have very high productivity, and so to reduce any bias from over-sampling of this region, the models were weighted according to the proportion of forest cover by Koeppen climate zone. 
ranch turnover. Any measures of primary productivity where components were unknown were excluded from analysis.
